---
title: "Assignment 1"
---

# Assignment 1

```{r}
1 + 1
```

My first assignment has three parts.

## (a)Video Selection

I have selected a video from Posit Youtube channel playlist which name is "Create & Publish a Quarto blog on Quarto Pub in 100 Seconds."

This video mainly focuses on creating a Quarto blog.

The steps are:

1.  R Studio---\> New project---\> New directory

2.  Quarto Blog---\>Directory name

3.  Build---\> Render website

4.  Terminal---\> "quarto publish"

## (b)Difference between R and Python

-   **Purpose:**

    R developed mainly for statistical analysis. Python is a general-purpose programming language.

-   **Community and Libraries:**

    Python offers libraries like Pandas, numpy,matplotlib. while R has comprehensive libraries (CRAN) for statistical tools.

-   **Syntax:**

    There are some major differences between R and Python in terms of syntax.

    -   Assignment Operator(=, \<-)

        ```{r}
        x<-5
        x
        ```

    -   Indexing

    -   Power Operator (\^,\*)

# **(c)**

```{r}
options(repos = c(CRAN = "https://cran.r-project.org"))
install.packages("dslabs")
```

```{r}
library(dslabs)
data("na_example")
na_example
```

```{r}
sum(is.na(na_example))
```

```{r}
no_na_example <- ifelse(is.na(na_example), 0, na_example)
no_na_example
```

```{r}
sum(is.na(no_na_example))
```
